Product graphics

### 2009-12-04 product-graphics.tex
Various tweaks

@@

\begin{itemize}
  \item \verb|~ a| represents $f(a)$,
  \item \verb|~ a + b| represents $f(a, b)$
  \item \verb!~ a | b! represents $f(a | b)$
\end{itemize}

@@

    \includegraphics[width=0.25\linewidth]{hb-vb-polar-2}%
    \includegraphics[width=0.25\linewidth]{hb-vs-polar-2}%
    \includegraphics[width=0.25\linewidth]{hs-hs-polar-2}%
    \includegraphics[width=0.25\linewidth]{hs-vs-polar-2}
  \caption{(Top) Area graphics in Cartesian coordinates.  (Mid) Area graphics in polar coordinates. (Bottom) Product graphics rotated 90 degrees before being converted to polar coordinates.  From left to right: hbar + hbar, , vspline + hbar, hspine + hspine, hspine + vspine.}
  \label{fig:polar}
\end{figure}

@@

We have assumed the probabilities represent counts, but without loss of generality we can use any set of non-negative, additive weights instead.  Some of the applications of such weighted plots are described in \citet{unwin:2007}.  Include a brief summary here.

>>>>

Some notation: let capital letters refer to the sample space, and lower case particular values.

@@

\begin{itemize}
  \item \verb|~ a| represents $f(a)$,
  \item \verb|~ a + b| represents $f(a, b)$
  \item \verb!~ a | b! represents $f(a | b)$
  \item \verb!~ . | a! is a special case of $f(a) = \frac{1}{\#A}$. 
\end{itemize}

@@

    \includegraphics[width=0.25\linewidth]{hb-vb-polar-2}%
    \includegraphics[width=0.25\linewidth]{hb-vs-polar-2}%
    \includegraphics[width=0.25\linewidth]{hs-hs-polar-2}%
    \includegraphics[width=0.25\linewidth]{hs-vs-polar-2}

  \caption{(Top) Area graphics in Cartesian coordinates. (Mid) Area graphics in polar coordinates. From left to right: hbar + hbar, vspline + hbar, hspine + hspine, hspine + vspine. (Bottom) Product graphics rotated 90 degrees before being converted to polar coordinates: vbar + vbar, hspline + vbar, vspine + vspine, vspine + hspine.}

  \label{fig:polar}
\end{figure}

@@

We have assumed the probabilities represent counts, but without loss of generality we can use any set of non-negative, additive weights instead. Some of the applications of such weighted plots are described in \citet{unwin:2007}. In the happy dataset, the {\sf wtssall} variable gives analytic survey weights. Figure~\ref{fig:weighting} shows the difference between the weighted and unweighted distributions of age and sex. The distribution is subtly different.

To express that we are displaying weights, rather than counts, we extend the formula syntax by putting the weighting variable on the left-hand side: $wtssall \sim sex + age$ vs. $ \sim sex + age$.

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{wt-count}%
    \includegraphics[width=0.5\linewidth]{wt-wtssall}%
  \caption{(Left) Unweighted distribution (counts).  (Right) Weighted by probability weights.}
  \label{fig:weighting}
\end{figure}
